---
title: "simpleRegress"
author: "Taelynn Condoll"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26

```{r}
lengthBears = predict(simp, newdata=data.frame(NECK=c(17,22,26)))
```


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```

The graph does not show a completely accurate line.

## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
chesty <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(chesty)
summary.lm(chesty)
```

The model chest has a slightly more accurate R-square of .79 whereas the model for neck was slightly lower at .75

```{r}
new <- data.frame(CHEST=c(17,22,26))
predict(chesty,new)
predict(chesty,new,se.fit=TRUE)
```

```{r}
chesty1 <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(chesty1)
summary.lm(chesty1)
```

The adjusted R-squared the model chest here is 0.50 and the model for NECk had an adjusted  R-square of 0.50. So far the best model is the one based on Chest. The best graph out of the last 2 is the first one.

```{r}
chesty2 <- lm(LENGTH~MONTH,data=bears)
plot(LENGTH~MONTH,data=bears)
abline(chesty2)
summary.lm(chesty2)
```

```{r}
chesty3 <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(chesty3)
summary.lm(chesty3)
```

The adjusted R-squared for chest here is 0.84 and the model for NECk is 0.80. The best model continues to be chest.

```{r}
chesty4 <- lm(LENGTH~SEX,data=bears)
plot(LENGTH~SEX,data=bears)
abline(chesty4)
summary.lm(chesty4)
```

The adjusted R-squared for both chest and NECk are -0.01. This graph does a good job of depicting the bear graph but its negative. This is the best so far.

```{r}
chesty5 <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(chesty5)
summary.lm(chesty5)
```


The adjusted R-squared for this model(chest) is 0.53; the model for NECk had an adjusted  R-square of 0.50. Therefore the best model continues to be the negative line graph.

```{r}
chesty6 <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(chesty6)
summary.lm(chesty6)
```
The adjusted R-squared for both chest and NECk are 0.75. This graph does a bad job of depicting the bear graph.

```{r}
chesty7 <- lm(LENGTH~LENGTH,data=bears)
plot(LENGTH~LENGTH,data=bears)
abline(chesty7)
summary.lm(chesty7)
```



```{r}
chesty8 <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(chesty8)
summary.lm(chesty8)
```

As you can see, headlength has the highest value, therefore headlength is the laargest. The best graph is the one that had a value of -0.01.
